True versus apparent shapes of bow shocks

### 2017-11-21 papers/Paper1/app-dust-wave.tex
Finish first draft of introduction to Paper 2

If the incoming dust grains initially travel along parallel
trajectories with varying \(b\), but the same \(v_\infty\), then deflection
by the radiative force will form a bow wave around the radiation
source, as shown in Figure~\ref{fig:dust-trajectories}.  However, the
inner edge of the bow wave, \(R_{\text{in}}(\theta)\) is not given by the
closest approach along individual trajectories, \(R\grain(\thm; b)\),
but instead must found by minimizing \(R\grain(\theta; b)\) over all
\(b\) for each value of \(\theta\), which yields
\begin{equation}
  \label{eq:dust-r-in}
  \frac{R_{\text{in}}(\theta)} {R_0} = \frac{2}{1 + \cos\theta} \ .
\end{equation}
This is the polar form of the equation for the confocal parabola,
which we have already discussed in detail in \S~\ref{sec:conic} and
Appendix~\ref{app:parabola}.  Its planitude and alatude are
\(\Gamma = \Lambda = 2\) and these are unchanged under projection at any
inclination.

@@

If the dust grains are assumed to originate from a second point
source, located at a distance \(D\) from the radiation source, then
the incoming stream will be divergent instead of plane parallel.  The
individual streamlines are not affected by this change and are still
described by equation~\eqref{eq:dust-r-theta}, except that the
trajectory axes for \(b > 0\) are no longer aligned with the global
symmetry axis, so we must make the substitution
\(\theta \to \theta + \theta_1(b)\), where \(\sin \theta_1 = b / D\) (see
Fig.~\ref{fig:crw-schema}). We parametrize the degree of divergence as
\(\mu = R_0 / D\) and, as before, \(R\grain(\theta + \theta_1(b, \mu); b)\) is
minimized over all trajectories to find the shape of the bow wave's
inner edge.  This time, the result is a confocal hyperbola:
\begin{equation}
  \label{eq:dust-divergent-r-in}
  \frac{R_{\text{in}}(\theta; \mu)} {R_0} = \frac{1 + \varepsilon_\mu}{1 + \varepsilon_\mu\cos\theta} \ ,
\end{equation}
where the eccentricity is (to first order in \(\mu\))
\( \varepsilon_\mu = (1 - 2\mu)^{-1}\).  An example is shown in
Figure~\ref{fig:dust-trajectories} for \(\mu = 0.1\).  Unsurprisingly,
the resulting bow shape is more open than in the parallel stream case,
increasingly so with increasing \(\mu\).  The planitude and alatude are
both equal: \(\Pi = \Lambda = 1 + \varepsilon_\mu\).

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/dragoid-R90-vs-Rc}
  \caption{Apparent projected shapes of dragoids in the
    \(\Pi'\)--\(\Lambda'\) plane. Colored symbols indicate the
    \(\abs{i} = 0\) position for selected models (see key).  Thin
    lines show the inclination-dependent tracks of each model, with
    tick marks along each track for 20 equal-spaced values of
    \(\abs{\sin i}\). Gray shaded regions are as in
    Fig.~\ref{fig:quadric-projection-continued}a.  The wilkinoid track
    is shown in white. }
  \label{fig:dragoid-Rc-R90}
\end{figure}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:

>>>>

If the incoming dust grains initially travel along parallel
trajectories with varying \(b\), but the same \(v_\infty\), then deflection
by the radiative force will form a bow wave around the radiation
source, as shown in Figure~\ref{fig:dust-trajectories}.  However, the
inner edge of the bow wave, \(R_{\text{in}}(\theta)\) is not given by the
closest approach along individual trajectories, \(R\grain(\thm; b)\),
but instead must found by minimizing \(R\grain(\theta; b)\) over all
\(b\) for each value of \(\theta\), which yields
\begin{equation}
  \label{eq:dust-r-in}
  \frac{R_{\text{in}}(\theta)} {R_0} = \frac{2}{1 + \cos\theta} \ .
\end{equation}
This is the polar form of the equation for the confocal parabola,
which we have already discussed in detail in \PaperI{}'s
\S~\ref{Q-sec:conic} and Appendix~\ref{Q-app:parabola}.  Its planitude
and alatude are \(\Gamma = \Lambda = 2\) and these are unchanged under projection
at any inclination.

@@

If the dust grains are assumed to originate from a second point
source, located at a distance \(D\) from the radiation source, then
the incoming stream will be divergent instead of plane parallel.  The
individual streamlines are not affected by this change and are still
described by equation~\eqref{eq:dust-r-theta}, except that the
trajectory axes for \(b > 0\) are no longer aligned with the global
symmetry axis, so we must make the substitution
\(\theta \to \theta + \theta_1(b)\), where \(\sin \theta_1 = b / D\) (see
Fig.~\ref{Q-fig:crw-schema} of \PaperI{}). We parametrize the degree
of divergence as \(\mu = R_0 / D\) and, as before,
\(R\grain(\theta + \theta_1(b, \mu); b)\) is minimized over all trajectories to
find the shape of the bow wave's inner edge.  This time, the result is
a confocal hyperbola:
\begin{equation}
  \label{eq:dust-divergent-r-in}
  \frac{R_{\text{in}}(\theta; \mu)} {R_0} = \frac{1 + \varepsilon_\mu}{1 + \varepsilon_\mu\cos\theta} \ ,
\end{equation}
where the eccentricity is (to first order in \(\mu\))
\( \varepsilon_\mu = (1 - 2\mu)^{-1}\).  An example is shown in
Figure~\ref{fig:dust-trajectories} for \(\mu = 0.1\).  Unsurprisingly,
the resulting bow shape is more open than in the parallel stream case,
increasingly so with increasing \(\mu\).  The planitude and alatude are
both equal: \(\Pi = \Lambda = 1 + \varepsilon_\mu\).

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/dragoid-R90-vs-Rc}
  \caption{Apparent projected shapes of dragoids in the
    \(\Pi'\)--\(\Lambda'\) plane. Colored symbols indicate the
    \(\abs{i} = 0\) position for selected models (see key).  Thin
    lines show the inclination-dependent tracks of each model, with
    tick marks along each track for 20 equal-spaced values of
    \(\abs{\sin i}\). Gray shaded regions are as in
    Fig.~\ref{Q-fig:quadric-projection-continued}a of \PaperI{}.  The
    wilkinoid track is shown in white. }
  \label{fig:dragoid-Rc-R90}
\end{figure}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "dusty-bow-wave"
%%% End:

### 2017-11-21 papers/Paper1/dusty-bow-wave.tex
Write first half of conclusions for Paper I
Paper 1 is finished!
Except I still need to finish the analytical calculation of the
wilkinoid projection at high inclination.  Currently I am just
guessing that it is (Pi-prime, Lambda-prime) = (3/2, sqrt(8/3))
Finish first draft of introduction to Paper 2

\usepackage{graphicx}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{fixltx2e}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{color}
\usepackage{enumerate}
\usepackage{pdflscape}
\usepackage{rotating}
\usepackage{hyperref}

@@

\title[Bow wave shapes]{True versus apparent shapes of dusty radiative bow waves}

@@

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\begin{abstract}
  Dusty stellar bow waves result from the action of a star's radiation
  pressure on a stream of dust grains that is flowing past it.  They
  are an alternative mechanism to hydrodynamic bow shocks for
  explaining the curved arcs of infrared emission seen around some
  stars.  We develop simple cylindrically symmetric models for the
  dust grain dynamics under the influence of radiation and gas--grain
  drag forces, which produce bow shapes that we call dragoids.  Using
  our recently developed two-dimensional classification scheme for
  projected bow shapes, we then analyze the inclination-dependent
  tracks of the dragoids in the planitude--alatude plane, finding
  interesting differences from the wilkinoid, cantoid, and ancantoid
  shapes of hydrodynamic bow shock models.  We analyze the prospects
  of using shape analysis of observational datasets to discriminate
  between different bow models, finding that sample sizes of order 100
  are required.
\end{abstract}

\begin{keywords}
  hydrodynamics -- stars: winds, outflows
\end{keywords}

\input{sec-dust-bow-intro}
\input{app-dust-wave}
\input{sec-standing-wave}
\bibliographystyle{mnras}
\bibliography{bowshocks-biblio}
\appendix
\input{app-dust-equations}

>>>>

\usepackage{graphicx}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{fixltx2e}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{color}
\usepackage{enumerate}
\usepackage{pdflscape}
\usepackage{rotating}
\usepackage{xr-hyper}
\usepackage{hyperref}
\externaldocument[Q-]{quadrics-bowshock}

@@

\title[Dusty bow wave shapes]
{True versus apparent shapes of dusty radiative bow waves}

@@

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\begin{abstract}
  Dusty stellar bow waves result from the action of a star's radiation
  pressure on a stream of dust grains that is flowing past it.  They
  are an alternative mechanism to hydrodynamic bow shocks for
  explaining the curved arcs of infrared emission seen around some
  stars.  We develop simple cylindrically symmetric models for the
  dust grain dynamics under the influence of radiation and gas--grain
  drag forces, which produce bow shapes that we call dragoids.  Using
  our recently developed two-dimensional classification scheme for
  projected bow shapes, we then analyze the inclination-dependent
  tracks of the dragoids in the planitude--alatude plane, finding
  interesting differences from the wilkinoid, cantoid, and ancantoid
  shapes of hydrodynamic bow shock models. We further show how these
  are modified in the presence of small-amplitude standing-wave
  oscillations of the basic shape, as may be produced by hydrodynamic
  instabilities or a time-varying source.  We analyze the prospects of
  using shape analysis of observational datasets to discriminate
  between different bow models, finding that sample sizes of order 100
  are required.
\end{abstract}

\begin{keywords}
  circumstellar matter -- radiation: dynamics -- stars: winds, outflows
\end{keywords}

\input{sec-dust-bow-intro}
\input{app-dust-wave}
\input{sec-standing-wave}
\input{sec-dust-bow-discuss}
\bibliographystyle{mnras}
\bibliography{bowshocks-biblio}
\appendix
\input{app-dust-equations}

### 2017-11-21 papers/Paper1/sec-conic.tex
Finish first draft of introduction to Paper 2

\begin{figure*}
  \setlength\tabcolsep{2em}
  \begin{tabular}{ll}
    (a) & (b) \\
    \includegraphics[height=0.45\linewidth]{figs/ellipse_edited}
        & \includegraphics[height=0.45\linewidth]{figs/hyperbola_edited}
  \end{tabular}
  \caption{Example off-center conic sections that can form quadrics of
    revolution: (a) ellipse, (b) hyperbola.  The relationship is shown
    between the conic section parameters \(a\), \(b\), \(\thetaQ\) and the
    bowshock characteristic radii \(R_0\), \(R_{90}\), \(R_c\), as
    defined in Fig.~\ref{fig:characteristic-radii}. The origin (center
    of the weaker flow) is indicated by a red star, the center of
    curvature of the apex of the bow shock is indicated by a green
    dot, and the geometric center of the conic section is indicated by
    a blue cross, which is offset by \(x_0\) from the origin.  Note
    that \(R_0\), \(R_{90}\), \(R_c\), \(a\), and \(b\) are all
    \emph{lengths} and are always positive, whereas \(x_0\) is a
    \emph{displacement} and may be positive or negative.}
  \label{fig:conics}
\end{figure*}
\begin{figure}
  \includegraphics[width=\linewidth]{figs/conic1}
  \caption{Example of a family of conic sections, all with the same
    planitude (flatness at apex, marked by white dot):
    \(\Pi = R_c/R_0 = 2 \). The quadric angle, \(\thetaQ\), varies over
    the family (see text), with lower values of \(\thetaQ\) giving
    larger values of the alatude, \(\Lambda = R_{90}/R_0 \), meaning more
    open wings.  Different values of \(\Pi\) can be achieved for the
    exact same quadrics by sliding them along the \(x\)-axis, which
    will also change the axis scales since these are normalized by
    \(R_0\).}
  \label{fig:conics-family}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/projected-R90-Rc-snapshots}
  \caption{Variation with inclination angle of the apparent shape of
    quadric bows with true planitude and alatude that are uniformly
    distributed over the ranges \(\Pi = [0.5, 4.5]\),
    \(\Lambda = [0.5, 4.5]\).  Panels show the apparent
    \((\Pi', \Lambda')\) as the inclination is increased through uniform
    intervals in \(\abs{sin i}\).  Symbol color represents the quadric
    parameter, \(\Q\), increasing from dark blue, through orange, to
    yellow. Symbol size is proportional to the increase in apparent
    star--apex distance, \(R_0'/R_0\).}
  \label{fig:projected-R90-Rc-snapshots}
\end{figure*}

>>>>

\begin{figure*}
  \setlength\tabcolsep{2em}
  \begin{tabular}{ll}
    (a) & (b) \\
    \includegraphics[height=0.45\linewidth]{figs/ellipse_edited}
        & \includegraphics[height=0.45\linewidth]{figs/hyperbola_edited}
  \end{tabular}
  \caption[]{Example off-center conic sections that can form quadrics of
    revolution: (a) ellipse, (b) hyperbola.  The relationship is shown
    between the conic section parameters \(a\), \(b\), \(\thetaQ\) and the
    bowshock characteristic radii \(R_0\), \(R_{90}\), \(R_c\), as
    defined in Fig.~\ref{fig:characteristic-radii}. The origin (center
    of the weaker flow) is indicated by a red star, the center of
    curvature of the apex of the bow shock is indicated by a green
    dot, and the geometric center of the conic section is indicated by
    a blue cross, which is offset by \(x_0\) from the origin.  Note
    that \(R_0\), \(R_{90}\), \(R_c\), \(a\), and \(b\) are all
    \emph{lengths} and are always positive, whereas \(x_0\) is a
    \emph{displacement} and may be positive or negative.}
  \label{fig:conics}
\end{figure*}
\begin{figure}
  \includegraphics[width=\linewidth]{figs/conic1}
  \caption[]{Example of a family of conic sections, all with the same
    planitude (flatness at apex, marked by white dot):
    \(\Pi = R_c/R_0 = 2 \). The quadric angle, \(\thetaQ\), varies over
    the family (see text), with lower values of \(\thetaQ\) giving
    larger values of the alatude, \(\Lambda = R_{90}/R_0 \), meaning more
    open wings.  Different values of \(\Pi\) can be achieved for the
    exact same quadrics by sliding them along the \(x\)-axis, which
    will also change the axis scales since these are normalized by
    \(R_0\).}
  \label{fig:conics-family}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/projected-R90-Rc-snapshots}
  \caption[]{Variation with inclination angle of the apparent shape of
    quadric bows with true planitude and alatude that are uniformly
    distributed over the ranges \(\Pi = [0.5, 4.5]\),
    \(\Lambda = [0.5, 4.5]\).  Panels show the apparent
    \((\Pi', \Lambda')\) as the inclination is increased through uniform
    intervals in \(\abs{sin i}\).  Symbol color represents the quadric
    parameter, \(\Q\), increasing from dark blue, through orange, to
    yellow. Symbol size is proportional to the increase in apparent
    star--apex distance, \(R_0'/R_0\).}
  \label{fig:projected-R90-Rc-snapshots}
\end{figure*}

### 2017-11-21 papers/Paper1/sec-dust-bow-intro.tex
Paper 1 is finished!
Except I still need to finish the analytical calculation of the
wilkinoid projection at high inclination.  Currently I am just
guessing that it is (Pi-prime, Lambda-prime) = (3/2, sqrt(8/3))
Finish first draft of introduction to Paper 2

\section{Introduction}
\label{sec:introduction}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

\defcitealias{Tarango-Yong:2018a}{Paper~I}
\newcommand\PaperI{\citetalias{Tarango-Yong:2018a}}

\section{Introduction}
\label{sec:introduction}
\newcommand\hii{\ion{H}{ii}}

Curved emission arcs around stars \citep[e.g.,][]{Gull:1979a} are
often interpreted as bow shocks, due to a supersonic hydrodynamic
interaction between the star's wind and an external stream. This
stream may be due to the star's own motion or to an independent flow,
such as an \hii{} region in the champagne phase
\citep{Tenorio-Tagle:1979a}, or another star's wind
\citep{Canto:1996}. However, an alternative interpretation in some
cases may be a radiation-pressure driven bow wave, as first proposed
by \citet[\S\textsc{vi}]{van-Buren:1988a}.  In this scenario, photons
emitted by the star are absorbed by dust grains in the incoming
stream, with the resultant momentum transfer being sufficient to
decelerate and deflect the grains within a certain distance from the
star, forming a dust-free, bow-shaped cavity with an enhanced dust
density at its edge.  Two regimes are possible, depending on the
strength of coupling between the gas (or plasma) and the dust.  In the
strong-coupling regime, gas--grain drag decelerates the gas along with
the dust, forming a shocked gas shell in a similar fashion to the
wind-driven bow shock case.  In the weak-coupling regime, the gas
stream is relatively unaffected and the dust temporarily decouples to
form a dust-only bow wave.  This second case has recently been studied
in detail in the context of the interaction of late O-type stars
(which have only weak stellar winds) with dusty photoevaporation flows
inside \hii{} regions \citep{Ochsendorf:2014a, Ochsendorf:2014b,
  Ochsendorf:2015a}.  More complex, hybrid scenarios are also
possible, such as that studied by \citet{van-Marle:2011a}, where a
hydrodynamic bow shock forms, but the larger dust grains that
accompany the stellar wind pass right through the shocked shell due to
weak gas--grain coupling, and form their own bow wave at a larger
radius.

In \citet[][hereafter \PaperI{}]{Tarango-Yong:2018a}, we proposed a
new two-dimensional classification scheme for bow shapes: the
projected planitude--alatude, or \(\Pi'\)--\(\Lambda'\), diagram.  Planitude
measures the flatness of the bow's apex, while alatude measures the
openness of the bow's wings.  Both are dimensionless ratios of lengths
that can be estimated from observational images.  We have analyzed the
inclination-dependent tracks on the \(\Pi'\)--\(\Lambda'\) plane for simple
geometric shapes (spheroids, paraboloids, hyperboloids) and for
thin-shell hydrodynamic bow shock models (wilkinoid, cantoids,
ancantoids).  In this paper, we will do the same for simple models of a
dusty radiation bow wave in the weak coupling limit (dragoids).

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "dusty-bow-wave"
%%% End:

### 2017-11-21 papers/Paper1/sec-intro.tex
Finish first draft of introduction to Paper 2

@@

The paper is organized as follows.
%
In \S~\ref{sec:plan-alat-bow} we outline the geometric parameters that
are necessary for describing bow shapes and introduce two
dimensionless ratios: planitude and alatude.
%
In \S~\ref{sec:projection} we derive general results for the
projection of bow shapes on to the plane of the sky.
%
In \S~\ref{sec:conic} we apply the results to the simplest possible
class of geometric bow models: the quadrics of revolution, which
comprise spheroids, paraboloids, and hyperboloids, each of which
occupies a disjoint region of the planitude--alatude plane.
%
In \S~\ref{sec:crw-scenario} we consider thin-shell hydrodynamic
models for the parallel-stream case (wilkinoids) and wind-wind case
(cantoids), including extension to an anisotropic inner wind
(ancantoids).  We calculate the location of the models in the
planitude--alatude plane as a function of the inclination of the bow
shock axis to the plane of the sky.
%
In \S~\ref{sec:conc} we summarise our results and outline how
following papers will apply these ideas to observations and numerical
simulations.

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/characteristic-radii}
  \caption{Parameters for characterizing a bow shape.  Bow radius from
    the star, measured parallel (\(R_0\)) and perpendicular
    (\(R_{90}\)) to the symmetry axis, together with radius of
    curvature (\(R_{\C}\)) at apex and asymptotic opening angle
    (\(\theta_\infty\)) of the far wings. }
  \label{fig:characteristic-radii}
\end{figure}

>>>>

% Force paper II to be before paper III in the reference list
\nocite{Henney:2018a}

@@

The paper is organized as follows.
%
In \S~\ref{sec:plan-alat-bow} we outline the geometric parameters that
are necessary for describing bow shapes and introduce two
dimensionless ratios: planitude and alatude.
%
In \S~\ref{sec:projection} we derive general results for the
projection of bow shapes on to the plane of the sky.
%
In \S~\ref{sec:conic} we apply the results to the simplest possible
class of geometric bow models: the quadrics of revolution, which
comprise spheroids, paraboloids, and hyperboloids, each of which
occupies a distinct region of the planitude--alatude plane.
%
In \S~\ref{sec:crw-scenario} we consider thin-shell hydrodynamic
models for the parallel-stream case (wilkinoids) and wind-wind case
(cantoids), including extension to an anisotropic inner wind
(ancantoids).  We calculate the location of the models in the
planitude--alatude plane as a function of the inclination of the bow
shock axis to the plane of the sky.
%
In \S~\ref{sec:conc} we summarise our results and outline how
following papers will apply these ideas to observations and numerical
simulations.

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/characteristic-radii}
  \caption[]{Parameters for characterizing a bow shape.  Bow radius
    from the star, measured parallel (\(R_0\)) and perpendicular
    (\(R_{90}\)) to the symmetry axis, together with radius of
    curvature (\(R_{\C}\)) at apex and asymptotic opening angle
    (\(\theta_\infty\)) of the far wings. }
  \label{fig:characteristic-radii}
\end{figure}

### 2017-11-21 papers/Paper1/sec-thin-shell.tex
Finish first draft of introduction to Paper 2

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/ancantoid-Pi-lambda-true}
  \caption{True shapes of cantoids and ancantoids in the
    \(\Pi\)--\(\Lambda\) plane, calculated according to results of
    App.~\ref{sec:thin-shell-shapes}.  For each line, \(\beta\) varies
    over the range \([0, 1]\) from lower left to upper right (although
    the black and red lines are truncated on the upper right), and
    line colors correspond to different anisotropy indices, matching
    those used in Fig.~\ref{fig:r-beta}. Circle symbols mark
    particular \(\beta\) values: \(0, 0.01, 0.1\), from largest to
    smallest circle.  Square symbols mark \(\beta = 0.5\), but with
    \(\Lambda\) calculated exactly, instead of using the approximation of
    equation~\eqref{eq:Lambda-approx}.  The white plus symbol marks
    the result for the wilkinoid:
    \((\Pi, \Lambda) = (\frac53, \sqrt{3})\).  Background shading indicates
    the domains of different quadric classes: hyperboloids (white),
    prolate spheroids (dark gray), and oblate spheroids (light gray).}
  \label{fig:ancantoid-Pi-lambda-true}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/ancantoid-angles}
  \caption{Equivalent quadric angles, \(\theta_{\Q}\), for ancantoids and
    cantoids.  Solid lines show values of \(\theta_{\Q}\) calculated from
    \((\Pi, \Lambda)\), which is representative of the shape of the head,
    while dashed lines show \(\theta_{\Q}\) calculated from
    \(\theta_\infty\), which is representative of the tail.  Dot-dashed line
    shows the result for cantoids, which differ from the \(k=0\)
    ancantoids in \(\theta_\infty\), but not in \((\Pi, \Lambda)\). Gray shading and
    line colors have the same meaning as in
    Fig.~\ref{fig:ancantoid-Pi-lambda-true}. }
  \label{fig:ancantoid-angles}
\end{figure}

@@

\begin{figure}
  \centering
  \setkeys{Gin}{width=\linewidth}
  \begin{tabular}{@{}l@{}}
    (a) \\
    \includegraphics{figs/ancantoid-R90-vs-Rc-a} \\
    (b) \\
    \includegraphics{figs/ancantoid-R90-vs-Rc-b}
  \end{tabular}
  \caption{Apparent projected shapes of wilkinoid, cantoids and
    ancantoids in the \(\Pi'\)--\(\Lambda'\) plane.  Colored symbols indicate
    the \(\abs{i} = 0\) position for \(\beta = 0.001\), \(0.003\),
    \(0.01\), \(0.03\), \(0.1\), \(0.3\).  Thin lines show the
    inclination-dependent tracks of each model, with tick marks along
    each track for 20 equal-spaced values of \(\abs{\sin i}\).  Gray
    shaded regions are as in
    Fig.~\ref{fig:quadric-projection-continued}a.  The wilkinoid track
    is shown in white. (a)~Isotropic wind model (cantoid) and
    proplyd-like model (ancantoid, \(k = 0.5\)). (b)~Hemispheric wind
    model (ancantoid, \(k = 0\)) and jet-like model (ancantoid,
    \(k = 3\)).}
  \label{fig:thin-shell-R90-Rc}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/ancantoid-R90-vs-Rc-lobeta-a}
  \caption{As Fig.~\ref{fig:thin-shell-R90-Rc}a but zoomed in to show
    the wilkinoid track (white) and the convergence of the cantoid
    tracks (purple) to the wilkinoid as \(\beta \to 0\).}
  \label{fig:convergence-cantoid-wilkinoid}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/ancantoid-Pi-lambda-true}
  \caption[]{True shapes of cantoids and ancantoids in the
    \(\Pi\)--\(\Lambda\) plane, calculated according to results of
    App.~\ref{sec:thin-shell-shapes}.  For each line, \(\beta\) varies
    over the range \([0, 1]\) from lower left to upper right (although
    the black and red lines are truncated on the upper right), and
    line colors correspond to different anisotropy indices, matching
    those used in Fig.~\ref{fig:r-beta}. Circle symbols mark
    particular \(\beta\) values: \(0, 0.01, 0.1\), from largest to
    smallest circle.  Square symbols mark \(\beta = 0.5\), but with
    \(\Lambda\) calculated exactly, instead of using the approximation of
    equation~\eqref{eq:Lambda-approx}.  The white plus symbol marks
    the result for the wilkinoid:
    \((\Pi, \Lambda) = (\frac53, \sqrt{3})\).  Background shading indicates
    the domains of different quadric classes: hyperboloids (white),
    prolate spheroids (dark gray), and oblate spheroids (light gray).}
  \label{fig:ancantoid-Pi-lambda-true}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/ancantoid-angles}
  \caption[]{Equivalent quadric angles, \(\theta_{\Q}\), for ancantoids and
    cantoids.  Solid lines show values of \(\theta_{\Q}\) calculated from
    \((\Pi, \Lambda)\), which is representative of the shape of the head,
    while dashed lines show \(\theta_{\Q}\) calculated from
    \(\theta_\infty\), which is representative of the tail.  Dot-dashed line
    shows the result for cantoids, which differ from the \(k=0\)
    ancantoids in \(\theta_\infty\), but not in \((\Pi, \Lambda)\). Gray shading and
    line colors have the same meaning as in
    Fig.~\ref{fig:ancantoid-Pi-lambda-true}. }
  \label{fig:ancantoid-angles}
\end{figure}

@@

\begin{figure}
  \centering
  \setkeys{Gin}{width=\linewidth}
  \begin{tabular}{@{}l@{}}
    (a) \\
    \includegraphics{figs/ancantoid-R90-vs-Rc-a} \\
    (b) \\
    \includegraphics{figs/ancantoid-R90-vs-Rc-b}
  \end{tabular}
  \caption[]{Apparent projected shapes of wilkinoid, cantoids and
    ancantoids in the \(\Pi'\)--\(\Lambda'\) plane.  Colored symbols indicate
    the \(\abs{i} = 0\) position for \(\beta = 0.001\), \(0.003\),
    \(0.01\), \(0.03\), \(0.1\), \(0.3\).  Thin lines show the
    inclination-dependent tracks of each model, with tick marks along
    each track for 20 equal-spaced values of \(\abs{\sin i}\).  Gray
    shaded regions are as in
    Fig.~\ref{fig:quadric-projection-continued}a.  The wilkinoid track
    is shown in white. (a)~Isotropic wind model (cantoid) and
    proplyd-like model (ancantoid, \(k = 0.5\)). (b)~Hemispheric wind
    model (ancantoid, \(k = 0\)) and jet-like model (ancantoid,
    \(k = 3\)).}
  \label{fig:thin-shell-R90-Rc}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/ancantoid-R90-vs-Rc-lobeta-a}
  \caption[]{As Fig.~\ref{fig:thin-shell-R90-Rc}a but zoomed in to show
    the wilkinoid track (white) and the convergence of the cantoid
    tracks (purple) to the wilkinoid as \(\beta \to 0\).}
  \label{fig:convergence-cantoid-wilkinoid}
\end{figure}
